---
title: "Datos"
description: |
  Aqui encontraras los datos relevantes para su consulta
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Descargar:
- Lorem ipsum.csv 

### Opción 1 de tabla
```{r}
library(knitr)
kable(head(mtcars))
```


### Opción 2 de tabla
```{r, layout="l-body-outset"}
library(rmarkdown)
paged_table(mtcars)
```


### Opción 3 de tabla
```{r, layout="l-body-outset"}
library(rmarkdown)
library(gt)
library(tidyverse)
library(glue)

# Define the start and end dates for the data range
start_date <- "2010-06-07"
end_date <- "2010-06-14"

# Create a gt table based on preprocessed
# `sp500` table data
sp500 %>%
  dplyr::filter(date >= start_date & date <= end_date) %>%
  dplyr::select(-adj_close) %>%
  gt() %>%
  tab_header(
    title = "S&P 500",
    subtitle = glue::glue("{start_date} to {end_date}")
  ) %>%
  fmt_date(
    columns = vars(date),
    date_style = 3
  ) %>%
  fmt_currency(
    columns = vars(open, high, low, close),
    currency = "USD"
  ) %>%
  fmt_number(
    columns = vars(volume),
    suffixing = TRUE
  )
```

### Tabla markdown

| Option           | Description                                    |
|------------------|------------------------------------------------|
| `rows.print`     | Maximum rows to print per page.                |
| `max.print`      | Maximum rows in the table (defaults to 1000).  |
| `cols.print`     | Maximum columns in the table (defaults to 10). |
| `rownames.print` | Print row names as part of the table.          |


### Tabla markdown 2\

::: l-body-outset
| Option           | Description                                    |
|------------------|------------------------------------------------|
| `rows.print`     | Maximum rows to print per page.                |
| `max.print`      | Maximum rows in the table (defaults to 1000).  |
| `cols.print`     | Maximum columns in the table (defaults to 10). |
| `rownames.print` | Print row names as part of the table.          |
:::
